---
title: "Sei's drum!"
author: "Michael Großbach"
date: Draft `r Sys.Date()`
output:
  html_document: 
    fig_caption: yes
    toc: yes
    toc_float: yes
    code_folding: hide
    fig_width: 3.5
bibliography: asiams.bib
editor_options:
    chunk_output_type: console
---

```{r Libraries, message=FALSE}
library(brms)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(kfigr)
library(knitr)
# library(pander)
library(patchwork)
# library(tidyr)
```

```{r Settings, echo=FALSE}
opts_chunk$set(comment = NULL,
               fig.width = 12,
               fig.height = 12, 
               echo = TRUE)
theme_set(theme_light())
knit_hooks$set(anchor = kfigr::hook_anchor)
opts_knit$set(kfigr.link = TRUE,
              kfigr.prefix = TRUE)
knitr::opts_chunk$set(fig.width = 3.5,
                      fig.height = 3.5)
options(mc.cores = parallel::detectCores())
rstan::rstan_options(auto_write = TRUE)
# Constants:
MODEL <- FALSE
FIGREF <- "Fig." # type for pics and plots, kfigr::figr()
TABREF <- "Tab." # type for tables, kfigr::figr()
MODREF <- "Model" # type for models, kfigr::figr()
PRIORREF <- "Prior" # type for priors, kfigr::figr()
SRCREF <- "Src." # type for source code blocks, kfigr::figr()
COLOR_BLIND_PALETTE <- RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")
source("dahl_drumming_models.R")
```

The data set was read in as is, the columns `subj`, `arm`, `cond`, `series` and `no` were converted to factors, the column `filename` was deleted.

```{r}
read.csv("features.csv") %>%
  mutate(filename = NULL,
         series = factor(series),
         subj = factor(subj),
         arm = factor(arm),
         cond = factor(cond),
         no = factor(no)) ->
  drum_beats
```

# Exploration

In a first attempt to get an overview, the descriptors' density estimates were plotted, broken down by `arm` and `cond`.

```{r DescriptorDensities, anchor=FIGREF, fig.width=12, fig.height=18}
dep_vars <- names(drum_beats)[which(!(names(drum_beats) %in% c("subj", 
                                                               "arm", 
                                                               "cond", 
                                                               "no",
                                                               "series")))]
n_vars <- length(dep_vars)
  plot_lst <- vector("list", length = n_vars)
  plt_cnt <- 1
  for (dv in dep_vars) {
    if (plt_cnt == n_vars) {
      plt_pos <- c(2, 0.5)
    } else {
      plt_pos <- "none"
    }
    if (plt_cnt %% 4 == 1) {
      ylab <- "density"
    } else {
      ylab <- ""
    }
    plot_lst[[plt_cnt]] <- ggplot(drum_beats, 
                                  aes_string(x = dv, 
                                             color = "cond")) +
      geom_density(na.rm = TRUE) + 
      scale_color_colorblind() +
      ylab(ylab) +
      geom_rug(alpha = 0.25) + 
      theme(legend.position = plt_pos) +
      facet_wrap(~ arm)
    plt_cnt <- plt_cnt + 1
  }
  print(wrap_plots(plot_lst, 
                   ncol = 4) +
          plot_annotation(
            tag_levels = "A"))
```

`r figr("DescriptorDensities", type = FIGREF)`. *Descriptor densities along with raw data points (rug ticks on x axes), broken down by arm (dominant [D] vs non-dominant [ND]) and instruction condition (controlled = C, normal = N).*

***

Several peculiarities are immediately apparent from the plots in `r figr("DescriptorDensities")`:

* There are no substantial differences in the density distributions between normal (N) and controlled (C) strokes
* `attDur`, `LAT`, and `attFlat` have very few unique data values (see rug ticks at bottom of plots)
* Looking at the dominant arm alone (and excluding the vars `attDur`, `LAT`, and `attFlat` for the reason just mentioned), the densities have a trend toward a larger variance in the controlled condition (in other words: a less pointed distribution)

The lack of any clear-cut differences in the raw data between conditions suggests that it will be hard to find any differences by modeling.

The limited number of unique values in the attack-related measures (*e.g.* `attDur` only has `r length(unique(drum_beats$attDur))` unique values in a total of `r nrow(drum_beats)` observations across all subjects, conditions, and sides; that's only `r round(length(unique(drum_beats$attDur)) / nrow(drum_beats) * 100)` percent!) suggests that rounding errors propagated through the calculations. This is probably due to very similar, *i.e.* highly automated, and short attack times combined with the given sampling frequency, resulting in few data points, which in course of the calculations result in the observed phenomenon. But I'm just guessing here, as I do not know anything about these descriptors and how they are calculated or interpreted. Judging by the range of values of, *i.e.*, `attDur` (`r round(range(drum_beats$attDur), 2)`ms, across both sides and conditions) and a sampling frequency of 48 kHz, this leaves us at 48 * (`r round(range(drum_beats$attDur), 2)[2]` - `r round(range(drum_beats$attDur), 2)[1]`) = `r round(48 * (range(drum_beats$attDur)[2] - range(drum_beats$attDur)[1]))` points to choose beginning and end of the attack. Given the supposed highly automatized motor program used to initiate the stroke, along with the laws of physics at play here (no pun intended), it is not very surprising to see very few unique values. My limited knowledge---or rather, my ignorance of anything sound-related---aside, from a statistical standpoint these measures do not seem suited to describe any differences between the experimental conditions investigated here. 

Given the very few data points in the attack phase, any descriptor derived from such a short period of time (*.e.g.*. `attSPL`) cannot be judged as being stable in the sense of being reproducible. Hence I suggest to drop all attack-derived descriptors.

```{r}
drum_beats %>%
  mutate(attDur = NULL,
         LAT = NULL,
         attSPL = NULL,
         attSC = NULL,
         attFlat = NULL,
         attSpecFlat = NULL) ->
  drum_beats
```

The increase in variance for the conditions N < C does not come as a surprise as I assume normal also means highly trained and thus automatized, whereas controlled involves less automatization and more 'individualness' both within and between subjects. 

## Conclusions

Looking at the above investigated descriptors and @Danielsen2015, it seems reasonable to limit the modeling attempts to `totDur`, `totSPL`, `totSC`, and `TC`.

# Model Considerations

There are several points that need to be considered before making a decision regarding the type of modeling to be done in this study, (1) the sample size places restrictions on the external validity; (2) data from small samples can be better modeled when regularization is in place to 'tame' the estimates; (3) the hierarchical structure of the data (subjects played several trials with either their dominant or non-dominat arm under two conditions) suggests a multilevel analysis of the data which would, in addition to the Bayesian regularization via priors also results in shrinkage of the estimates; (4) given the small distribution differences between the two experimental conditions in the varying variance between conditions

Given the extremely small sample size, any attempt to fit the data using traditional statistics, a.k.a. null-hypothesis significance testing, would make us vulnerable to all kinds of criticism. I therefor suggest to use Bayesian statistics instead, as it allows us to estimate probability distributions of parameters rather than confidence intervals around point estimates, and thus embraces uncertainty in estimates. 

Additionally, Bayesian regression uses prior probability distributions to arrive at sensible estimates. These priors regularize estimates, or draw them toward zero, a desirable effect which has long been recognized even in traditional statistics (*e.g.* ridge regression and lasso; @Tibshirani1996).

ANOVA (or regression with grouping variables) requires each subject's trials to be averaged, say, within conditions or groups (or both), to be able to assess treatment effects; this results in the individual variation within a subject to get lost while it might have been very informative to include it in the analysis. Multilevel (or hierarchical) modeling allows to include the entire data structure (`r figr("MLMstructure", type = FIGREF)`) so that no information gets lost through averaging, but all variation (both individual and treatment-driven) propagates through the analysis and ends up in the final results, allowing for more realistic credibility margins around estimates. 

```{r MLMstructure, anchor=FIGREF}
# chunk intentionally empty  
```

~~~
Instruction:    Normal        			Controlled
                | |    \      			/ |    \
Player:         1 2 ... n			   1  2 ... n
               / \
Side   dominant non-dominant
        / | \	    / | \
Trial  1 ..  p     1  .. p
~~~

`r figr("MLMstructure")`. *The multilevel structure of a data set should be reflected in the analysis.*

***

Also, the variation in traditional statistics is considered to be fixed (think homoscedasticity in ANOVA, or the $\epsilon$ in regression formulas such as $y_i = \beta_0 + \beta_1x_i + \epsilon_i$), whereas it is an estimated quantity in Bayesian statistics and therefor can vary between conditions (or groups or subjects etc.). 

## Conclusions

Will start with a simple univariate model, add predictors and interactions, then a bivariate model, and finally a quadruple-variate model and see where this leads us.

# Modeling

The hypothesis is that 

## Simple Univariate Models

Looking again at the variables *I* have decided to use as response variables in the regression models---implying that this is by no means set in stone---, it seems like a skewed normal link function would be appropriate to model them.

Let's start with `totDur`. Using an extended model description language [@Bates2010;@Buerkner2018], going back to Wilkinson and Rogers's [-@Wilkinson1973] modeling language, we write:

```{r}
(m0_form <-bf(totDur ~ 1 + (1 | subj)))
```

which claims that `totDur` is explained by ('~') an intercept, denoted by '1', and an additional term '(1 | subj)'. The '1' in parentheses again stands for the intercept, but the pipe '|' assigns an intercept to each level of the factor 'subj'. In this particular case this means that the model will estimate an individual intercept for each unique drummer listed in the data set column `subj`. These individual, or varying, intercepts are then used in informing the estimation of the population intercept. 

```{r}
if (MODEL) {
  m0 <- brm(m0_form,
            family = skew_normal(),
            data = drum_beats)
  m0 <- add_criterion(m0, 
                      "loo",
                      reloo = TRUE)
  save(m0, 
       file = "m0.rda")
} else {
  load("m0.rda")
}
```

This null model is also termed unconditional model because it has no grouping structure apart from individuals--the 'subj' bit in the model equation above. There is some variation in every natural data set. To make sure, it's not just variation caused by different participants, we can calculate the intra-class correlation coefficient (ICC).

```{r}
m0_icc <- ICC(m0, "subj")
```

The Null model's ICC amounts to `r round(m0_icc, 2)`, which suggests that approx. `r round(m0_icc, 1) * 100` percent of the variation in the data set can be attributed to (or explained by) the grouping structure. This is highly unfortunate, as it does not leave a lot of variation to be explained by independent factors like instruction, or arm. The most likely reason for this high ICC value is the small sample size combined with high inter-individual variation. Small sample sizes combined with large trial numbers are less of a problem when subjects respond, on average, close to the population mean, even with large spread due to fluctuating alertness, increasing fatigue etc., *.e.g.* in reaction time paradigms. But here, with large intra- *and* inter-individual variation, this might become a problem.

***

`r figr("m0_summary", type = TABREF)`. *Model summary.*

```{r m0_summary, achor = TABREF}
(m0_summary <- summary(m0, 
                       priors = TRUE))
```

The intercept in `r figr("m0_summary")` amounts to roughly `r round(m0_summary$fixed["Intercept", "Estimate"])`ms. In this model specification, the intercept is identical to the data set average. The table also shows that the interindividual standard deviation (`sd(Intercept)`) is large compared to the unexplained variation (`sigma`). This led to the large ICC value above. By adding more and more independent factors to the model specification, we will later try to decrease $\sigma$, *i.e.* 'explain away' as much remaining variation as possible. 

```{r m0_ppcheck, anchor=FIGREF}
pp_check(m0, nsamples = 100)
```

`r figr("m0_ppcheck", type = FIGREF)`. *Posterior predictive check. The thick blue line shows the distribution of the empirical data. The thin blue lines are one-hundred realizations of data generated from parameters estimated by the model.*

***

The posterior predictive plot in `r figr("m0_ppcheck")` gives an impression on how the null model would generate data, given the parameters it estimated from the empirical data. As the thick line deviates from the modeled thin lines, especially on the left side and the peak of the distribution, it is apparent that the model can be improved. It must be noted though, that for a null model the posterior predictive check is surprisingly good--yet another sign that the high ICC value poses a problem.

```{r}
# conditional_effects(m0) 
```


# System Setup

Data wrangling and analyses were carried out with the statistical package `R` [`r version$version.string`; @RCT2020]. Bayesian modeling was done with the package `brms` [@Buerkner2017;@Buerkner2018] which uses the probabilistic language Stan as back end [@Carpenter2017]. Plots were done with the packages `bayesplot` [@Gabry2020] and `ggplot2` [@Wickham2016].

# References 
